---
title: "RWorksheet#5"
author: "Quebral, Francisco, Marquez"
date: "2024-11-19"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```






```{r}
url <- "https://www.imdb.com/chart/toptv/?ref_=nv_tvv_250c"
```







```{r}
page <- read_html(url)
```

```{r}
library(httr)
library(dplyr)
library(rvest)
rows <-  page %>%
  html_nodes('h3.ipc-title__text') %>% 
  html_text()
rows
```
```{r}

rows <- as.data.frame(rows)
 Titles <- rows[-c(1, nrow(rows)), ]

Titles
```

```{r}
ratings <- page %>% html_nodes("span.ipc-rating-star--rating")  %>%  html_text()
ratings <- as.data.frame(ratings)
ratings
```

```{r}
The_number_of_people_voted <- page %>% html_nodes("span.ipc-rating-star--voteCount")  %>%  html_text()
The_number_of_people_voted <- as.data.frame(The_number_of_people_voted)
The_number_of_people_voted
```

```{r}
episodes <- page %>% html_nodes("span.sc-5bc66c50-6.OOdsw.cli-title-metadata-item")  %>%  html_text()  

episode_numbers <- str_extract(episodes, "\\d+ eps")


episode_numbers <- str_remove(episode_numbers, " eps")


episode_numbers <- as.data.frame(episode_numbers)
episode_numbers <- episode_numbers[!is.na(episode_numbers)]
print(episode_numbers)
```

```{r}
episodes <- page %>% html_nodes("span.sc-5bc66c50-6.OOdsw.cli-title-metadata-item") %>% html_text()


year_data <- str_extract(episodes, "\\d{4}")


year_data <- year_data[!is.na(year_data)]


year_data <- as.numeric(year_data)

print(year_data)
```

```{r}
Imdb <- data.frame(Titles,ratings,The_number_of_people_voted,episode_numbers,year_data)
Imdb

```
#2. From the 50 tv shows, select at least 5 tv shows to scrape 20 user reviews that will include the reviewer’s name, date of reviewed, user rating, title of the review, the numbers for “is helpful” and “is not helpful”, and text reviews.
```{r}
link <-  "https://www.imdb.com/title/tt5491994/reviews/?ref_=tt_urv_sm"
link1 <- "https://www.imdb.com/title/tt0185906/reviews/?ref_=tt_urv_sm"
link2 <- "https://www.imdb.com/title/tt7366338/reviews/?ref_=tt_urv_sm"
link3 <- "https://www.imdb.com/title/tt0306414/reviews/?ref_=tt_urv_sm"
link4 <- "https://www.imdb.com/title/tt0417299/reviews/?ref_=tt_urv_sm"
window <- read_html(link)
window1 <- read_html(link1)
window2 <- read_html(link2)
window3 <- read_html(link3)
window4 <- read_html(link4)
```
```{r}
Reviewers_name <-  window %>%
  html_nodes("a.ipc-link.ipc-link--base") %>% 
  html_text()

Reviewers_names <- Reviewers_name[Reviewers_name != "Permalink"]
Reviewers_names[c(1:20)]
```
```{r}
Date_of_Reviewed <-  window %>%
  html_nodes("li.ipc-inline-list__item.review-date") %>% 
  html_text()

Date_of_Reviewed[c(1:20)]
```
```{r}
Ratings <-  window %>%
  html_nodes("span.ipc-rating-star--rating") %>% 
  html_text()

Ratings[c(1:20)]
```
```{r}
Title <-  window %>%
  html_nodes("h3.ipc-title__text") %>% 
  html_text()

as.data.frame(Title)
Title[c(1:20)]
```
```{r}

Helpful <- window %>%
  html_nodes("span.ipc-voting__label__count.ipc-voting__label__count--up") %>%
  html_text()
Helpful[c(1:20)]
```

```{r}
Not_Helpful <- window %>%
  html_nodes("span.ipc-voting__label__count ipc-voting__label__count--up")  %>%
  html_text()
  
Not_Helpful[c(1:20)]
```

```{r}
Review_text <- window %>% 
   html_nodes("div.ipc-html-content-inner-div")  %>%
  html_text()
Review_text[c(1:20)]
```

```{r}
Reviewers_name1 <-  window1 %>%
  html_nodes("a.ipc-link.ipc-link--base") %>% 
  html_text()

Reviewers_name1 <- Reviewers_name1[Reviewers_name1 != "Permalink"]
Reviewers_name1[c(1:20)]
```
```{r}
Date_of_Reviewed1 <-  window1 %>%
  html_nodes("li.ipc-inline-list__item.review-date") %>% 
  html_text()

Date_of_Reviewed1[c(1:20)]
```
```{r}
Ratings1 <-  window1 %>%
  html_nodes("span.ipc-rating-star--rating") %>% 
  html_text()

Ratings1[c(1:20)]
```
```{r}
Title1 <-  window1 %>%
  html_nodes("h3.ipc-title__text") %>% 
  html_text()

Title1[c(1:20)]
```
```{r}
Helpful1 <- window1 %>%
  html_nodes("scan.ipc-voting__label__count ipc-voting__label__count--up") %>%
  html_text()
Helpful1[c(1:20)]
```
```{r}
Not_Helpful1 <- window1 %>%
  html_nodes("span.ipc-voting__label__count ipc-voting__label__count--up")  %>%
  html_text()
Not_Helpful1[c(1:20)]
```
```{r}
Review_text1 <- window1 %>% 
   html_nodes("div.ipc-html-content-inner-div")  %>%
  html_text()
Review_text[c(1:20)]
```
```{r}
Reviewers_name2 <-  window2 %>%
  html_nodes("a.ipc-link.ipc-link--base") %>% 
  html_text()

Reviewers_names2<-Reviewers_name2[Reviewers_name2 != "Permalink"]
Reviewers_names2[c(1:20)]
```
```{r}
Date_of_Reviewed2 <-  window2 %>%
  html_nodes("li.ipc-inline-list__item.review-date") %>% 
  html_text()

Date_of_Reviewed2[c(1:20)]
```
```{r}
Ratings2 <-  window2 %>%
  html_nodes("span.ipc-rating-star--rating") %>% 
  html_text()

Ratings2[c(1:20)]
```
```{r}
Title2 <-  window2 %>%
  html_nodes("h3.ipc-title__text") %>% 
  html_text()


Title2[c(1:20)]
```
```{r}
Helpful2 <- window2 %>%
  html_nodes("scan.ipc-voting__label__count ipc-voting__label__count--up") %>%
  html_text()
Helpful2[c(1:20)]
```

```{r}
Not_Helpful2 <- window2 %>%
  html_nodes("span.ipc-voting__label__count ipc-voting__label__count--up")  %>%
  html_text()
Not_Helpful2[c(1:20)]
```
```{r}
Review_text2 <- window2 %>% 
   html_nodes("div.ipc-html-content-inner-div")  %>%
  html_text()
Review_text2[c(1:20)]
```
```{r}
Reviewers_name3 <-  window3 %>%
  html_nodes("a.ipc-link.ipc-link--base") %>% 
  html_text()

Reviewers_names3 <- Reviewers_name3[Reviewers_name3 != "Permalink"]
Reviewers_names3[c(1:20)]
```
```{r}
Date_of_Reviewed3 <-  window3 %>%
  html_nodes("li.ipc-inline-list__item.review-date") %>% 
  html_text()

Date_of_Reviewed3[c(1:20)]
```
```{r}
Ratings3 <-  window3 %>%
  html_nodes("span.ipc-rating-star--rating") %>% 
  html_text()

Ratings3[c(1:20)]
```
```{r}
Title3 <-  window3 %>%
  html_nodes("h3.ipc-title__text") %>% 
  html_text()

Title3[c(1:20)]
```
```{r}
Helpful3 <- window3 %>%
  html_nodes("scan.ipc-voting__label__count ipc-voting__label__count--up") %>%
  html_text()
Helpful3[c(1:20)]
```

```{r}
Not_Helpful3 <- window3 %>%
  html_nodes("span.ipc-voting__label__count ipc-voting__label__count--up")  %>%
  html_text()
Not_Helpful3[c(1:20)]
```

```{r}
Review_text3 <- window3 %>% 
   html_nodes("div.ipc-html-content-inner-div")  %>%
  html_text()
Review_text3[c(1:20)]
```

```{r}
Reviewers_name4 <-  window4 %>%
  html_nodes("a.ipc-link.ipc-link--base") %>% 
  html_text()

Reviewers_names4 <-Reviewers_name4[Reviewers_name4 != "Permalink"]
Reviewers_names4[c(1:20)]
```
```{r}
Date_of_Reviewed4 <-  window4 %>%
  html_nodes("li.ipc-inline-list__item.review-date") %>% 
  html_text()

Date_of_Reviewed4[c(1:20)]
```
```{r}
Ratings4 <-  window4 %>%
  html_nodes("span.ipc-rating-star--rating") %>% 
  html_text()

Ratings4[c(1:20)]
```
```{r}
Title4 <-  window4 %>%
  html_nodes("h3.ipc-title__text") %>% 
  html_text()


Title4[c(1:20)]
```
```{r}
Helpful4 <- window4 %>%
  html_nodes("scan.ipc-voting__label__count ipc-voting__label__count--up") %>%
  html_text()
Helpful4
```
```{r}
Not_Helpful4 <- window4 %>%
  html_nodes("span.ipc-voting__label__count ipc-voting__label__count--up")  %>%
  html_text()
Not_Helpful4
```
```{r}
Review_text4 <- window4 %>% 
   html_nodes("div.ipc-html-content-inner-div")  %>%
  html_text()
Review_text4
```
#3. Create a time series graph for the tv shows released by year. Which year has the most number of tv shows released?
```{r}

tv_data_grouped <- Imdb %>%
  group_by(year_data) %>%
  summarize(Titles = n())

ggplot(tv_data_grouped, aes(x = year_data, y = Titles)) +
  geom_line() +
  geom_point() +
  labs(x = "Year", y = "Number of TV Shows", title = "TV Shows Released by Year") +
  theme_minimal()
```

#AMAZON
#4. Select 5 categories from Amazon and select 30 products from each category.


```{r}
library(rvest)
library(dplyr)
library(polite)

url <- "https://www.amazon.com/s?k=Laptop&ref=nav_bb_sb"

page1 <- read_html(url)

```
5. Extract the price, description, ratings and reviews of each product.
```{r}

titles <- page1 %>% html_nodes(".a-size-medium") %>% html_text(trim = TRUE)
prices <- page1 %>% html_nodes(".a-price-whole") %>% html_text(trim = TRUE)
ratings <- page1 %>% html_nodes(".a-icon-alt") %>% html_text(trim = TRUE)
reviews <- page1 %>% html_nodes(".s-link-style") %>% html_text(trim = TRUE)
```

```{r}
max_length <- max(length(titles), length(prices), length(ratings), length(reviews))

titles <- c(titles, rep(NA, max_length - length(titles)))
prices <- c(prices, rep(NA, max_length - length(prices)))
ratings <- c(ratings, rep(NA, max_length - length(ratings)))
reviews <- c(reviews, rep(NA, max_length - length(reviews)))

ama1 <- data.frame(
  Title = titles,
  Price = as.numeric(gsub(",", "", prices)),
  Ratings = as.numeric(gsub(" out of 5 stars", "", ratings)),
  Reviews = as.integer(gsub(",", "", reviews))
)



as.data.frame(ama1)
```

